---
title: "DATA607Project2"
author: "jim lung"
date: "03-11-2017"
output: html_document
---


```{r}
library(dplyr)
library(tidyr)
library(knitr)
library(ggplot2)
library(plotly)

```

Wide data set 1 - New_York_City_Leading_Causes_of_Death

The source: https://data.cityofnewyork.us/Health/New-York-City-Leading-Causes-of-Death/jb7j-dtam/data


```{r }
causeofdeath<-read.csv("~/New_York_City_Leading_Causes_of_Death.csv")
glimpse(causeofdeath)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

```{r }
library(stringr)
causedeath <- causeofdeath %>% rename("Leading_Cause"=Leading.Cause, "Race_Ethnicity"=Race.Ethnicity, "Death_Rate"=Death.Rate, "Age_Adjusted_Death_Rate"=Age.Adjusted.Death.Rate)


head(causedeath)

```

```{r }

cause2012<- causedeath %>%
  filter(Year == "2012") %>%
  group_by(Year, Race_Ethnicity) %>%
  select(Year, Sex, Leading_Cause, Race_Ethnicity, Deaths,Death_Rate, Age_Adjusted_Death_Rate)
head(cause2012)

```

```{r }

kable(causedeath %>% 
           select(Year, Sex, Leading_Cause, Death_Rate) %>% 
           group_by(Year, Sex) %>% 
           select(Year, Sex, Leading_Cause, Death_Rate) %>% 
          arrange(Death_Rate) %>%
          top_n(1))

```

```{r }
library(plotly)

ggplotly(ggplot(cause2012,aes(x=Race_Ethnicity,y=Age_Adjusted_Death_Rate))+geom_bar(aes(fill=Sex),stat="identity",position="dodge")+ylab("Death Rate")+ggtitle("Race_Ethnicity"))


```


Wide data set 2 - Total world population

The source: http://data.worldbank.org/indicator/SP.POP.TOTL

```{r }
population<-read.csv("~/population.csv", skip = 4)
glimpse(population)
```

```{r }
population$Indicator.Name<-NULL
population$Indicator.Code<-NULL
population$X<-NULL
population$X2016<-NULL
population <- population[complete.cases(population), ] 
head(population)

```

Using Tidyr function:
```{r }
tpopulation <- population %>%
                      gather(group, "population", -Country.Code, -Country.Name) %>% 
                      separate(group, c("X", "Year"), sep="X") %>% 
                      select(-X) %>% 
                      arrange(Country.Code, Year)

tpopulation$Year <- as.numeric(tpopulation$Year)

tpopulation <- as.data.frame(tpopulation)

tpopulation
```
Analysis for max and min of population:
```{r }
population_percent <- tpopulation %>%
                   na.omit() %>%   #omit the na value
                   group_by(Country.Code) %>% #Group country for comparing
                   mutate(min_year = min(Year), max_year = max(Year)) %>%  #calculate min and max number
                   filter(Year == min_year | Year == max_year) %>%  #Year can be "min" or "max"
                   mutate(rn = str_c("Y", row_number())) %>% # labelling M1 and M2 for min and max
                   select(Country.Name, Country.Code, population, rn) %>%
                   spread(rn, population) %>%      # Separate M1 and M2 for min and max
                   rename(Min.Year=Y1, Max.Year=Y2) %>%
                   mutate(Percent.Change = round(((Max.Year - Min.Year)/Min.Year) * 100, 2)) 


population_percent <- as.data.frame(population_percent)
population_percent

```

Summary of max and min percentage change:

```{r }
comparecountry <- filter(population_percent, Percent.Change==min(Percent.Change) |Percent.Change==max(Percent.Change))

kable(comparecountry)

```


Wide data set 3 - Lottery-Cash-4-Life-Winning-Numbers

The source: https://data.ny.gov/Government-Finance/Lottery-Cash-4-Life-Winning-Numbers-Beginning-2014/kwxv-fwze


```{r }
lottery<-read.csv("~/lottery.csv")
glimpse(lottery)
```

```{r }
dlottery <- lottery %>%
                      separate(Draw.Date, c("Month","Day","Year"), sep="/") %>%
                      separate(Winning.Numbers, c("N1","N2","N3","N4","N5")) %>%
                      gather(lottery,"Number", 4:9) %>%
                      arrange(Year,Month,Day)

dlottery$Month <- as.numeric(dlottery$Month)
dlottery$Day <- as.numeric(dlottery$Day)
dlottery$Year <- as.numeric(dlottery$Year)

dlottery <- as.data.frame(dlottery)

dlottery
```


```{r }
library(plotly)
ggplot(dlottery, aes(x = Year, y=Number)) + coord_flip() + geom_bar(stat="identity") + xlab("Year") + ylab("Number") 
```
